Rapid technological progress in white light-emitting diodes \\ and its sources in innovation and technology spillovers

### 2024-03-16 2_SSL_NE/article/article_main.tex
updated supplementary information introduction

M.P. Weinold$^{1,2,3}$, S. Kolesnikov$^1$, L.D. Anadon$^{1,4}$ \\
\newline
$^1$ Centre for Environment, Energy and Natural Resource Governance, Department of Land Economy, University of Cambridge, Cambridge, UK \\
$^2$ Group for Energy Systems Analysis, Department of Mechanical and Process Engineering, ETH Zurich, Zurich, Switzerland \\
$^3$ Technology Assessment Group, Paul Scherrer Institute, Villigen, Switzerland \\
$^4$ Belfer Center for Science and International Affairs, Harvard University, Cambridge MA, USA

>>>>

M.P. Weinold$^{1,2,3}$, S. Kolesnikov$^1$, L.D. Anadon$^{1,4}$ \\
\newline
$^1$ Centre for Environment, Energy and Natural Resource Governance Department of Land Economy, University of Cambridge, Cambridge, UK \\
$^2$ Group for Energy Systems Analysis, Department of Mechanical and Process Engineering, ETH Zurich, Zurich, Switzerland \\
$^3$ Technology Assessment Group, Paul Scherrer Institute, Villigen, Switzerland \\
$^4$ Belfer Center for Science and International Affairs, Harvard University, Cambridge MA, USA

### 2024-03-16 2_SSL_NE/article/article_supplementary.tex
updated supplementary information introduction

\setlength{\fboxsep}{10pt}
\fbox{
    \parbox{\textwidth}{
        \textit{\textsc{Supplementary Information}} for: \\
        \newline 
        M.P. Weinold$^{1,2,3}$, S. Kolesnikov$^1$, L.D. Anadon$^{1,4}$ \\
        \newline
        $^1$Centre for Environment, Energy and Natural Resource Governance \\ Department of Land Economy, University of Cambridge, Cambridge, UK \\
        $^2$Group for Energy Systems Analysis, Department of Mechanical and Process Engineering \\ ETH Zurich, Zurich, Switzerland \\
        $^3$Technology Assessment Group, Paul Scherrer Institute  Villigen, Switzerland \\
        $^4$Belfer Center for Science and International Affairs, Harvard University, Cambridge MA, USA
    }
}

\clearpage
\tableofcontents

>>>>

\setlength{\fboxsep}{10pt}
\fbox{
    \parbox{\textwidth}{
        \textit{\textsc{Supplementary Information}} for: \\
        \newline 
        \textbf{Rapid technological progress in white light-emitting diodes\\
        and its sources in innovation and technology spillovers} \\
        \newline
        M.P. Weinold$^{1,2,3}$, S. Kolesnikov$^1$, L.D. Anadon$^{1,4}$ \\
        \newline
        $^1$Centre for Environment, Energy and Natural Resource Governance \\
        \hspace*{0.7mm} Department of Land Economy, University of Cambridge, Cambridge, UK \\
        $^2$Group for Energy Systems Analysis \\
        \hspace*{0.7mm} Department of Mechanical and Process Engineering, ETH Zurich, Zurich, Switzerland \\
        $^3$Technology Assessment Group, Paul Scherrer Institute  Villigen, Switzerland \\
        $^4$Belfer Center for Science and International Affairs, Harvard University, Cambridge MA, USA
    }
}

\tableofcontents
